---
title: "Reproducible Pitch Presentation"
author: "KARTHIK Theivendran"
highlighter : highlight.js
date: "29 July 2018"
output: 
  ioslides_presentation: 
    incremental: yes
job : "Reproducible Pitch Presentation"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Reproducible Pitch



URL: <https://github.com/karthikmca39/Data-Products-Shiny-Application>

Find here all the data that have been use for this presentation and also for the first part of the data Science Project. "First, i have created a Shiny application and deploy it on Rstudio's servers.Second, i used Rstudio Presenter to prepare a reproducible pitch presentation about your application."

See the Regression Models Course Project

Find all details here :
URL: <https://class.coursera.org/devdataprod-007>
URL: <https://class.coursera.org/devdataprod-007/human_grading/view/courses/972606/assessments/5/submissions>



## mtcars dataset

Motor Trend Car Road Tests :
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

Source :
Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.
```{r echo = TRUE}
library(datasets)
head(mtcars, 3)
```


## mtcars dataset - Format

A data frame with 32 observations on 11 variables.

- mpg: Miles/(US) gallon
- cyl: Number of cylinders
- disp: Displacement (cu.in.)
- hp: Gross horsepower
- drat: Rear axle ratio
- wt: Weight (1000 lbs)
- qsec: 1/4 mile time
- vs: V/S
- am: Transmission (0 = automatic, 1 = manual)
- gear: Number of forward gears
- carb: Number of carburetors


## Analysis - main code


formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
    
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)  })
    
  
  output$fit <- renderPrint({
    summary(fit()) })
    
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })  })



